---
title: "A04_G42955089"
author: "Jiwei Zeng"
date: "September 29, 2017"
output: html_document
---

```{r}
library(dplyr)
library(tibble)
library(xtable)
library(ggplot2)
## Part A

# Read the data
mydf <- read.csv("HR_comma_sep.csv")

# get rows and columns
dim.data.frame(mydf)

# explore the data structure
str(mydf)

# Correlate all the numeric fields
xtable(cor(subset(mydf, select = -c(sales, salary))))


# Create a correlation heat map
library(reshape2)
melted_cormat <- melt(cor(subset(mydf, select = -c(sales, salary))))
head(melted_cormat)

g <- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_raster()
g <- g + theme(axis.text.x = element_text(angle = 90, hjust = 1))
g


# Develop a 3-way table
mydf$status <- ifelse(mydf$left == 1, "Left", "Stay")
table(mydf$status,  mydf$salary, mydf$sales)


# Employees who leave by department
ggplot(mydf[ which(mydf$status=='Left'),], aes(x = sales, fill = status)) + geom_bar() + guides(fill=FALSE) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) 


```

```{r}
# Employees who stay by department

ggplot(mydf[ which(mydf$status=='Stay'),], 
       aes(x = sales, fill = status)) + geom_bar() + guides(fill=FALSE) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

```{r}
#Part B

#Employees who leave the company by salary level

ggplot(mydf[ which(mydf$status=='Left'),], aes(x = salary, fill = status)) + geom_bar() + guides(fill=FALSE) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

```{r}
#Employees who stay the company by salary level

ggplot(mydf[ which(mydf$status=='Stay'),], aes(x = salary, fill = status)) + geom_bar() + guides(fill=FALSE) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

```{r}
# Make a chart for number of employees who leave the company by time spent in the company
# faceted by salary level AND department

ggplot(mydf[ which(mydf$status=='Left'),], aes(x = time_spend_company, fill = status)) + geom_bar() + guides(fill=FALSE) +theme(axis.text.x = element_text(hjust = 1)) + facet_grid(sales~salary)
```

```{r}
# Make a chart for number of employees who stay in the company by time spent in the company
# faceted by salary level AND department

ggplot(mydf[ which(mydf$status=='Stay'),], aes(x = time_spend_company, fill = status)) + geom_bar() + guides(fill=FALSE) +theme(axis.text.x = element_text(hjust = 1)) + facet_grid(sales~salary)
```

```{r}
## Part C
# Draw a bar plot of how many years did employees stay in the company before leaving
# Year stayed in the company is the x axis
ggplot(mydf[ which(mydf$status=='Left'),], aes(x = time_spend_company, fill = status)) + geom_bar() + guides(fill=FALSE) +theme(axis.text.x = element_text(hjust = 1))

```
```{r}
# Draw a bar plot of how many years did employees stay in the company before leaving
# by department
# Year stayed in the company is the x axis
ggplot(mydf[ which(mydf$status=='Left'),], aes(x = time_spend_company, fill = status)) + geom_bar() + guides(fill=FALSE) +theme(axis.text.x = element_text(hjust = 1)) + facet_grid(sales~.)
```

```{r}
# Draw a bar plot of how many years did employees stay in the company before leaving
# by salary level
# Year stayed in the company is the x axis

ggplot(mydf[ which(mydf$status=='Left'),], aes(x = time_spend_company, fill = status)) + geom_bar() + guides(fill=FALSE) +theme(axis.text.x = element_text(hjust = 1)) + facet_grid(salary~.)
```


Note:


Ggplot is very useful in data visualization. We can change our plots according to our needs, no matter how complicated our needs are. I believe it amazing to explore the possability of ggplot.


According to the plots, we can know that those departments, which more employees stay in, have higher number of people leaving. Those who have low salary in the company are more willing to leave. Besides, most of those who decide to leave always have stayed in the company for less 5 years.