---
title: "A03a_G42955089"
author: "Jiwei Zeng"
date: "September 20, 2017"
output: html_document
---
Part A

a.

```{r}
mydf <- read.csv("households.csv",header = TRUE)
library(plyr)
library(dplyr)
glimpse(mydf)
```

b.

Family.size: ordinal
It is an categorial variable and it can order by size of the family, so it should be ordinal.

Location:nominal
It is an unordered categorial variable, so it should be difined as nominal.

Ownership:nominal
It is an unordered categorial variable, so it should be difined as nominal.

c.

```{r}
hist(mydf$Family.Size)
#It is skewed to the right.
```

```{r}
hist(mydf$First.Income)
#It is skewed to the right.
```
```{r}
hist(mydf$Second.Income)
#It is skewed to the right.
```
```{r}
hist(mydf$Monthly.Payment)
#It is skewed to the right.
```
```{r}
hist(mydf$Utilities)
#It is skewed to the left.
```
```{r}
hist(mydf$Debt)
#It is skewed to the right.
```

d.

```{r}
max(mydf$Debt)
#So the maximum debt levels is 9104.
```
```{r}
min(mydf$Debt)
#So the minimum debt levels is 227.
```

e.

The indebtedness levels at each of the 25th, 50th, and 75th percentiles:
```{r}
quantile(mydf$Debt,probs = seq(0.25,0.75,0.25))
```

f.

The interquartile range is 5675.5-2948.5=2727. The result is small, which means the data of the debt is skewed.

g.

The income of most families is lower than the mean of income. Also, most of their monthly payment and debt is lower than the mean. The credit risk is low.
